Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Final pass through Results.

The overall size of the data was 10mb and came from Boston-area hospitals and is subject to data use agreements. The training data consisted of 170 medical records and the test data consisted of 256 medical records. Further, the distribution over labels of the training and test sets is provided in Figure~\ref{fig:data_set_counts}.

@@

We deployed the system on a machine running Ubuntu 11.10 with a QuadCore AMD Opteron processor running a 2.5Ghz and 48GB of ram.

@@

Overall we found that our system did a good job at predicting labels for medical notes. Figure~\ref{fig:all_confusion_matrix} shows a confusion matrix of a model that was trained with all features enabled and Figure~\ref{fig:all_features_results} shows summary statistics for that very same model. The results are broken down so we can see the relative performance of each of the individual classifiers. Overall, the system does very well and achieves an average F1-score of {\bf 0.79}.

>>>>

The overall size of the data was 10mb and came from Boston-area hospitals--so it is subject to data use agreements. The training data consisted of 170 medical records and the test data consisted of 256 medical records. Further, the distribution over labels of the training and test sets is provided in Figure~\ref{fig:data_set_counts}.

@@

We deployed the system on a machine running Ubuntu 11.10 with a QuadCore AMD Opteron processor running a 2.5Ghz and 48GB of RAM.

@@

Overall we found that our system did a good job at predicting labels for medical notes. Figure~\ref{fig:all_confusion_matrix} shows a confusion matrix of a model that was trained with all features enabled and Figure~\ref{fig:all_features_results} shows summary statistics for that very same model. The results are broken down so we can see the relative performance of each of the individual classifiers. Overall, the system does very well and achieves an average F1-score of about {\bf 0.80}.
